Hybrid platforms and bargaining power

### 2023-04-09 src/paper/application.tex
Fix hagiu reference

Hybrid platforms also received increasing attention in the literature.
While not explicitly phrased in terms of hybrid operation, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
These papers mostly focus on competition between platforms, and not on the impact on the platform-participant relationship.
On the other hand, more recent papers, such as \textcite{hagiu2020should}, \textcite{anderson2021hybrid} and \textcite{gutierrez2021welfare} have started to address the issue of hybrid platforms, and how platforms having their own products affect competition between the platform and the entrants, and ultimately consumer welfare and producer surplus.
The results are mixed: while some of them find that hybrid platforms can be beneficial if certain anti-competitive behavior, such as self-preferencing, is prevented \parencite[]{anderson2021hybrid}, others are more critical of this hybrid form \parencite[]{anderson2021hybrid}.
This paper provides some additional insights into this topic, by looking at the impact of dual mode operation on bargaining power.

>>>>

Hybrid platforms also received increasing attention in the literature.
While not explicitly phrased in terms of hybrid operation, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
These papers mostly focus on competition between platforms, and not on the impact on the platform-participant relationship.
On the other hand, more recent papers, such as \textcite{hagiu2022should}, \textcite{anderson2021hybrid} and \textcite{gutierrez2021welfare} have started to address the issue of hybrid platforms, and how platforms having their own products affect competition between the platform and the entrants, and ultimately consumer welfare and producer surplus.
The results are mixed: while some of them find that hybrid platforms can be beneficial if certain anti-competitive behavior, such as self-preferencing, is prevented \parencite[]{anderson2021hybrid}, others are more critical of this hybrid form \parencite[]{anderson2021hybrid}.
This paper provides some additional insights into this topic, by looking at the impact of dual mode operation on bargaining power.
